### 2014-10-31 fundamentals/intro.tex
went with essential instead of major

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables major capabilities that previous 
simulators lack. First, its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangeability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
emphasizes applicability of the \Cyclus tool across a broader range of 
fidelities, scales, and applications than other simulators.

>>>>

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables essential capabilities that previous 
simulators lack. First, its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangeability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
emphasizes applicability of the \Cyclus tool across a broader range of 
fidelities, scales, and applications than other simulators.
